\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Avaneesh Singh} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91-8953999885 \\ Pune, India} 
\address{\href{mailto:avaneeshsingh1999@gmail.com}{avaneeshsingh1999@gmail.com} \\ \href{https://linkedin.com/company/faangpath}{Linkedin} \\ \href{https://github.com/avaneesh1999}{Github}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Software Engineer with 2+ years of experience in XXX, seeking full-time XXX roles.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Computer Science}, DR. A.P.J. ABDUL KALAM TECHNICAL UNIVERSITY \hfill { 2021}\\
Cum. GPA: 8.2 /10\\
Relevant Coursework: A, B, C, and D.

{\bf CLASS XII}, SUMITRA PUBLIC INTER COLL. \hfill {2017}\\
PERCENTAGE-84
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages  & Java, Python,C,SQL,Javascript
\\
Technologies and Frameworks & AWS, Azure,Azure Data Factory,Linux, DevOps Tools, Git,Docker, Kubernetes\\
Certifications & AZ-900, Snow-pro, NPTEL Python Programming,Freecodecamp Javascript\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Associate Consultant -2} \hfill Sep 2021 - Current\\
EVIDEN \hfill \textit{Pune, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Achieved 55\% growth for CUNA Mutual Group using Azure, SQL, and DevOps skills.also spot recognizition award from EVIDEN for my performance. 
     \item Migrated a on-prem server using application to azure,which saved 1000+ hours of work per month.
     \item Automated ADF and Azure Portal processes by developing custom Python scripts and integrating with SQL database; saved 30+ hours of manual work per week and increased task accuracy by 95\%.
    \item devloped a pipeline to deploy a production application on AKS(Azure Kubernetes service) which automated the manual process and increased project accuracy by 75\%. 
 \end{itemize}
 
% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{GFG-SCRAPER} {Created a tool which Converts Data Structure questions of GeeksforGeeks
website into a excel file with Question Name and link .Created using Automation with Javascript ,Puppeteer and Node.js.Consist of functionalities like Searching problems on GeeksforGeeks by tag
names,Create Directory and Excel file.}
\item \textbf{Cloud Migration of On-premise Web Application to Azure.} {Designed an Azure infrastructure architecture that included Azure App Service, Azure SQL Database, Azure Blob Storage, and Azure Virtual Network to migrate on prem web application to azure.}
\item \textbf{Deployment of a Web Application to Azure Kubernetes Service (AKS).} {Build a project that Containerized the web application using Docker, creating Docker images for the application and its dependencies.used Azure tools to deploy it on AKS}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize} 
    \item  I have been an active member of my local cricket club and organization cricket club for last couple of years,  participating in regular matches and tournaments.also won many man of the matches awards for my team.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership} 
\begin{itemize}
    \item Admin for the {College Coding community} with over 1000+ job seekers and Students. Actively involved in facilitating  career conversations and job opportunities alongside other admins and a team of volunteer moderators! 
\end{itemize}


\end{rSection}


\end{document}
